|

### 2023-01-31 paper.Rmd
Tue Jan 31 17:00:08 CET 2023: update-remote.sh

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models $M_g$. Figure \@ref(fig:airfoil-trainingEpochs) shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore have positive benefit on the runtime of DAE-GP.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model $M_G$, we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \@ref(fig:airfoil-SamplingTime) shows the median sampling time spend during each generation of the search and it clearly shows that pre-training does strongly increase the time spent on model sampling in comparison to regular DAE-GP

>>>>

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models $M_g$. Figure \@ref(fig:airfoil-trainingEpochs) shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore have a positive benefit on the runtime of DAE-GP.

@@

If we look at another time consuming operation in DAE-GP, the creation of new individuals by sampling the DAE-LSTM model $M_G$, we see one main reason for the large runtime increase by pre-training DAE-GP. Figure \@ref(fig:airfoil-SamplingTime) shows the median sampling time spend during each generation of the search and it clearly demonstrates that pre-training does strongly increase the time spent on model sampling  in comparison to regular DAE-GP. The median time spend on sampling new individual for regular DAE-GP increases by a factor of `r round(PT_MEDIAN_SAMPLINGTIME / REG_MEDIAN_SAMPLINGTIME, 3)` from `r format(REG_MEDIAN_SAMPLINGTIME, scientific=F)` to `r format(REG_MEDIAN_SAMPLINGTIME, scientific=F)`
